Effectiveness of community-based TURF-reserves in Mexican small-scale fisheries

### 2019-02-11 docs/SupplementaryMaterial.Rmd
Added changes for Rev1

```{r}
conapesca %>% 
  mutate(price = valor / peso_vivo) %>% 
  group_by(zona, grupo, post, unidad_economica) %>% 
  summarize(price = mean(price, na.rm = T)) %>% 
  ungroup() %>% 
  spread(post, price) %>% 
  knitr::kable(digits = 2,
               col.names = c("Zone", "Group", "TURF", "Before", "After"),
               caption = "Mean ex-vessel prices for lobster (Panulirus spp.) on each TURF (community) by zone (MC = Caribbean; PN = Pacific) and group (Control = only TURF, Treated = TURF and reserve).",
               booktabs = T)
```

```{r, fig.cap = "Time series of landings and value of landings."}
valor <- conapesca %>% 
  ggplot(aes(x = years_centered, y = valor / 1000, color = grupo)) +
  facet_wrap(~ zona, ncol = 2, scales = "free_y")  +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.1, size = 1) +
  stat_summary(geom = "line", fun.y = mean) +
  stat_summary(geom = "point", fun.y = mean, size = 2) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1", direction = -1) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  ylab("Value (K MXP)") +
  xlab("") +
  guides(color = guide_legend(title = "", ncol = 2)) +
  theme(legend.justification = c(0,0),
        legend.position = c(0.55, 0.7)) +
  geom_vline(xintercept = 0, linetype = "dashed", size = 1)

peso <- conapesca %>% 
  ggplot(aes(x = years_centered, y = peso_vivo / 1000, color = grupo)) +
  facet_wrap(~ zona, ncol = 2, scales = "free_y")  +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.1, size = 1) +
  stat_summary(geom = "line", fun.y = mean) +
  stat_summary(geom = "point", fun.y = mean, size = 2) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1", direction = -1) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  ylab("Landings (Tones)") +
  xlab("Year since implementation") +
  theme(legend.position = "none") +
  geom_vline(xintercept = 0, linetype = "dashed", size = 1)

cowplot::plot_grid(valor, peso, ncol = 1)

>>>>

```{r}
conapesca %>% 
  filter(!unidad_economica == "jose maria azcorra") %>% 
  mutate(price = valor / peso_vivo) %>% 
  group_by(zona, grupo, post, unidad_economica) %>% 
  summarize(price = mean(price, na.rm = T)) %>% 
  ungroup() %>% 
  spread(post, price) %>% 
  mutate(zona = ifelse(zona == "MC", "Yucatan Peninsula", "Baja California"),
         unidad_economica = taxize::taxize_capwords(unidad_economica)) %>% 
  knitr::kable(digits = 2,
               col.names = c("Community", "Group", "TURF", "Before", "After"),
               caption = "Mean ex-vessel prices (MXP / Kg) for lobster (Panulirus spp.) on each TURF (community) and group (Control = only TURF, Treated = TURF and reserve).",
               booktabs = T)
```

```{r, fig.cap = "Time series of landings and value of landings."}
valor <- conapesca %>% 
  filter(!unidad_economica == "jose maria azcorra") %>% 
  mutate(zona = ifelse(zona == "MC", "Yucatan Peninsula", "Baja California")) %>% 
  ggplot(aes(x = years_centered, y = valor / 1000, color = grupo)) +
  facet_wrap(~ zona, ncol = 2, scales = "free_y")  +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.1, size = 1) +
  stat_summary(geom = "line", fun.y = mean) +
  stat_summary(geom = "point", fun.y = mean, size = 2) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1", direction = -1) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  ylab("Value (K MXP)") +
  xlab("") +
  guides(color = guide_legend(title = "", ncol = 2)) +
  theme(legend.justification = c(0,0),
        legend.position = c(0.55, 0.7)) +
  geom_vline(xintercept = 0, linetype = "dashed", size = 1)

peso <- conapesca %>% 
  filter(!unidad_economica == "jose maria azcorra") %>% 
  ggplot(aes(x = years_centered, y = peso_vivo / 1000, color = grupo)) +
  facet_wrap(~ zona, ncol = 2, scales = "free_y")  +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.1, size = 1) +
  stat_summary(geom = "line", fun.y = mean) +
  stat_summary(geom = "point", fun.y = mean, size = 2) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1", direction = -1) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  ylab("Landings (Tones)") +
  xlab("Year since implementation") +
  theme(legend.position = "none") +
  geom_vline(xintercept = 0, linetype = "dashed", size = 1)

cowplot::plot_grid(peso, valor, ncol = 1)
